Resolving the measurement uncertainty paradox in ecological management

### 2018-12-28 manuscripts/manuscript.tex
add license and citation to code repo

We consider the average fish biomass across 100 replicate simulations of
the same stock dynamics (Eq 4) under three different management
strategies: constant escapement (CE), total allowable catch (TAC; equal
to 80\% MSY), and partially observed Markov decision process (POMDP)
management. Each suite of simulations is considered under three
sequentially higher measurement error regimes, from \(\sigma_m = 0\) (no
measurement errors), \(\sigma_m = 0.1\) (low error), and
\(\sigma_m = 0.15\) (moderate error), as indicated, while stochastic
recruitment (environmental noise) is set to a moderate
\(\sigma_g = 0.15\). Empirical estimates of measurement error in stock
sizes vary widely, with estimates often dependent upon methodological
assumptions. Early estimates have put possible error as high as 50\%
(Clark and Kirkwood 1986) and more recent analyses have suggested an
average of closer to 36\%, though with cases that may be much higher
(Ralston et al. 2011). Consequently, range between 0 to 15\% provides a
probably conservative estimate of typical uncertainty ranges, which we
show is nevertheless large enough to drive substantially negative
ecological and economic outcomes under management strategies that do not
appropriately account for that error over the long run.

@@

@@

>>>>

We consider the average fish biomass across 100 replicate simulations of
the same stock dynamics (Eq 4) under three different management
strategies: constant escapement (CE), total allowable catch (TAC; equal
to 80\% MSY), and partially observed Markov decision process (POMDP)
management. Each suite of simulations is considered under three
sequentially higher measurement error regimes, from \(\sigma_m = 0\) (no
measurement errors), \(\sigma_m = 0.1\) (low error), and
\(\sigma_m = 0.15\) (moderate error), as indicated, while stochastic
recruitment (environmental noise) is set to a moderate
\(\sigma_g = 0.15\). Empirical estimates of measurement error in stock
sizes vary widely, with estimates often dependent upon methodological
assumptions. Early estimates have put possible error as high as 50\%
(Clark and Kirkwood 1986) and more recent analyses have suggested an
average of closer to 36\%, though with cases that may be much higher
(Ralston et al. 2011). Consequently, range between 0 to 15\% provides a
probably conservative estimate of typical uncertainty ranges, which we
show is nevertheless large enough to drive substantially negative
ecological and economic outcomes under management strategies that do not
appropriately account for that error over the long run. We provide
complete code and data files to reproduce the analysis shown here in the
Appendices and as research compendium (Marwick et al. 2018) at
\url{https://github.com/boettiger-lab/pomdp-intro}, archived at
(Boettiger and Memarzadeh 2018).

@@

\leavevmode\hypertarget{ref-pomdp-intro}{}%
Boettiger, C., and M. Memarzadeh. 2018. Supplement to: "Resolving the
measurement uncertainty paradox in ecological management". Zenodo.

@@

\leavevmode\hypertarget{ref-Marwick2018}{}%
Marwick, B., C. Boettiger, and L. Mullen. 2018. Packaging Data
Analytical Work Reproducibly Using R (and Friends). The American
Statistician 72:80--88.
